Scikit-learn: machine learning without learning the machinery

### 2014-05-21 article.tex
Finish pass on text example

\paragraph{A simple text-mining example.}
%
Not every dataset comes as a set of numbers. For instance in natural
language processing (NLP), each observation is a text, \emph{i.e.} a
string, that needs to be transformed into the data matrix expected by
estimators. Typical, features used to build decisions indicate the
presence of certain words, and often their frequencies.
In spam filtering, it can very relevant to extract from a document that
it contains the term \textsf{viagra}, and possibly how many times.
In other NLP problems such as finding proper names,
events such as ``next token is the Roman numeral'' may be relevant, as in
``J.P. Kennedy III''. Counting bigrams, or $n$-grams, can be a way of
capturing this information. Reusing the {\tt transform} API, scikit-learn
provide a few \emph{feature extraction} objects, that can turn such
unstructured data into a data matrix.
The $\textbf{X}$ matrix is in these situations a
matrix of counting statistics. It is full of zeros, in the sens that very
often a word is present only in a few documents. For better scalability,
it can be encoded using SciPy's sparse matrices, that many scikit-learn
estimators process efficiently.

@@

Does this classifier work?
We can find out by classifying two of our own movie reviews.\footnote{
  The code can be tried interactively by simply copy-pasting it
  into an interactive Python interpreter or IPython \cite{perez2007ipython}.
}

\begin{lstlisting}
>>> clf.predict(["Worst movie I ever saw",
...      "Godzilla, eat your heart out!"])
array([0, 1])
\end{lstlisting}

Here, we asked the model to predict the probability of a review being positive
for a batch of two reviews. It returns the negative probability in the first
column, the positive probability in the second.
As we can see, the first review gets a 99.9\% probability for being negative,
while the second has an 83\% probability of being positive.

Of course, that's just anecdotal evidence. We can get a figure for the
classifier's accuracy by retraining it in a five-fold cross-validation scheme:

\begin{lstlisting}
>>> from sklearn import cross_validation
>>> cross_validation.cross_val_score(clf, data.data, data.target)
array([ 0.91, 0.8825, 0.88, 0.8775, 0.86])
\end{lstlisting}

>>>>

\paragraph{A simple text-mining example.}
%
Not every dataset comes as a set of numbers. For instance in natural
language processing (NLP), each observation is a text, \emph{i.e.} a
string, that needs to be transformed into the data matrix expected by
estimators. Typical, features used to build decisions indicate the
presence of certain words, and often their frequencies.
In spam filtering, it can very relevant to extract from a document that
it contains the term \textsf{viagra}, and possibly how many times.
In other NLP problems such as finding proper names,
events such as ``next token is the Roman numeral'' may be relevant, as in
``J.P. Kennedy III''. Counting bigrams, or $n$-grams, can be a way of
capturing this information. Reusing the {\tt transform} API, scikit-learn
provide a few \emph{feature extraction} objects, that can turn such
unstructured data into a data matrix. In these situations, the
$\textbf{X}$ matrix is a
matrix of counting statistics. It is full of zeros, in the sens that very
often a word is present only in a few documents. For better scalability,
it can be encoded using SciPy's sparse matrices, that many scikit-learn
estimators process efficiently.

@@

We can test our classifier on two new movie reviews.\footnote{
  The code can be tried interactively by simply copy-pasting it
  into an interactive Python interpreter or IPython \cite{perez2007ipython}.
}
\begin{lstlisting}
>>> clf.predict(["Worst movie I ever saw",
...      "Godzilla, eat your heart out!"])
array([0, 1])
\end{lstlisting}

Here, we asked the estimator to predict if the reviews were positive for
a batch of two reviews. The first review is predicted has being not
positive, \emph{i.e.} negative, while the second one is positive. We have
anecdotal evidence that the classifier work. To get a measure for the
classifier's accuracy we retraining it in a cross-validation scheme, this
yield the fraction of correct answers on three different folds:
\begin{lstlisting}
>>> from sklearn import cross_validation
>>> cross_validation.cross_val_score(clf, data.data, data.target)
array([0.9026946, 0.8723724, 0.8633634])
\end{lstlisting}
